Fig1

### 2020-05-06 analysis/figure-1.Rmd
bigger font

d1 <- sexbarplots(hypsex, 0, 7000) + labs(y = "DEGS", subtitle = "hypothalamus" )
d2 <- sexbarplots(pitsex, 0, 7000) + labs(subtitle = "pituitary" ) + 
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(), axis.ticks = element_blank())
d3 <- sexbarplots(gonsex, 0, 7000) + labs(subtitle = "gonads" ) +
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(), axis.ticks = element_blank())

>>>>

d1 <- sexbarplots(hypsex, 0, 7100) + labs(y = "DEGS", subtitle = "hypothalamus" )
d2 <- sexbarplots(pitsex, 0, 7100) + labs(subtitle = "pituitary" ) + 
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(), axis.ticks = element_blank())
d3 <- sexbarplots(gonsex, 0, 7100) + labs(subtitle = "gonads" ) +
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(), axis.ticks = element_blank())
